Deep Reinforcement Learning for Conservation Decisions

### 2021-05-27 manuscript/manuscript.Rmd
Adding citations

<!-- reason 1: generalizability-->
<!-- ML: pivoting this to generalizability but still rewrote past paragraph which might fit in the appendix somewhere-->
Currently, deep RL agents struggle to generalize their skills [@generalization].
This inability can affect performance during training and at evaluation. 
For instance, training an agent on an environment that demands learning an assortment of skills is typically much more difficult than training an agent to learn one specific skill [@CITE].
And, at evaluation, if you give an agent a novel task, including tasks that are closely related to the examples that the agent saw in training, the agent can easily fail to generalize its learned behavior to this new situation [@CITE].
These failures are all due to the brittleness of deep neural networks. 
Across deep learning, neural networks tend to perform exceptionally well on narrowly defined problems, yet neural networks show great fragility when given new situations or problem statements that require flexibility [@CITE].
The ability to adapt to new situations is critical for any decision-making problem in the real world, so the current lack of this ability in deep RL may limit deep RL's effectiveness to conservation problems.

<!--
Under some conditions, RL agents can prove adept at _transfer learning_, in which an agent trained in one environment performs well under a different environment.
-->
<!-- if we're really recommending 'testing' for stability, maybe we need to demo that in the appendix-->
<!-- reason 2: interpretability -->
Deep RL agents are also very difficult to interpret [@cite].
Deep neural networks are commonly referred to as black box models, since it is not possible to fully explain why a deep neural network produces a specific output from a given input [@cite].
For deep RL, this means that we cannot provide a meaningful explanation for why any agent selects an action.
Compounded with the previously mentioned generalizability issues, the lack of explainability introduces a lot of safety concerns when attempting to apply these methods to the real world.
When going from a simulator to the real world, the real world may introduce novel situations that a simulator-trained agent is not familiar with, and since we can't anticipate how an agent will respond to new situations, there is an inherent risk in letting RL agents make decisions in the real world.

<!-- reason 3: reward design -->
And lastly, a fundamental issue for all applied optimization problems is using the right objective.
There have been many examples in which explicit reward design produces unanticipated agent behavior that is highly undesirable [@CITE].
Thus, for ecological systems, which are typically quite difficult to control, specifying a reward function could easily produce behavior that opposes the intents of the RL practitioner.
To guide agents to learn desirable policies, RL researchers often *shape* the reward function so that the agent will more readily learn certain behaviors[@cite].
This approach is particularly common when rewards are *sparse*, which occurs when there are few state-action pairs that have strong feedback signals.
Frequently, when researchers do not shape the rewards on sparse reward problems, the RL agent learns nothing [@CITE], but reward shaping can still backfire by producing unintended agent behavior [@CITE]. 
Given the nature of many conservation problems, where benefits rarely come immediately and thus the reward structures are sparse, RL agents will likely have difficulty learning anything, or, in the case that researchers shape the rewards to aid learning, the agents may learn policies that are undesirable.
Moreover, specifying a reward function for conservation brings up various ethical concerns.
E.g., who gets to specify the reward function, and will the values of the greater community be represented in the reward function?

>>>>

<!-- reason 1: generalizability-->
<!-- ML: pivoting this to generalizability but still rewrote past paragraph which might fit in the appendix somewhere-->
Currently, deep RL agents struggle to generalize their skills [@pmlr-v97-cobbe19a].
This inability can affect performance during training and at evaluation. 
For instance, training an agent on an environment that demands learning an assortment of skills is typically much more difficult than training an agent to learn one specific skill [@teh_distral_2017].
And, at evaluation, if you give an agent a novel task, including tasks that are closely related to the examples that the agent saw in training, the agent can easily fail to generalize its learned behavior to this new situation [@pmlr-v97-cobbe19a].
These failures are all due to the brittleness of deep neural networks. 
Across deep learning, neural networks tend to perform exceptionally well on narrowly defined problems, yet neural networks show great fragility when given new situations or problem statements that require flexibility [@cogswell_reducing_2016].
The ability to adapt to new situations is critical for any decision-making problem in the real world, so the current lack of this ability in deep RL may limit deep RL's effectiveness to conservation problems.

<!--
Under some conditions, RL agents can prove adept at _transfer learning_, in which an agent trained in one environment performs well under a different environment.
-->
<!-- if we're really recommending 'testing' for stability, maybe we need to demo that in the appendix-->
<!-- reason 2: interpretability -->
Deep RL agents are also difficult to interpret [@heuillet_explainability_2021].
Deep neural networks are commonly referred to as black box models, since it is challenging to fully explain why a deep neural network produces a specific output from a given input [@castelvecchi_can_2016].
For deep RL, this means that we cannot provide a meaningful explanation for why any agent selects an action.
Compounded with the previously mentioned generalizability issues, the lack of explainability introduces a lot of safety concerns when attempting to apply these methods to the real world.
When going from a simulator to the real world, the real world may introduce novel situations that a simulator-trained agent is not familiar with, and since we can't anticipate how an agent will respond to new situations, there is an inherent risk in letting RL agents make decisions in the real world.

<!-- reason 3: reward design -->
And lastly, a fundamental issue for all applied optimization problems is using the right objective.
There have been many examples in which explicit reward design produces unanticipated agent behavior that is highly undesirable [@hadfield-menell_inverse_2020].
Thus, for ecological systems, which are typically quite difficult to control, specifying a reward function could easily produce behavior that opposes the intents of the RL practitioner.
To guide agents to learn desirable policies, RL researchers often *shape* the reward function so that the agent will more readily learn certain behaviors [@reward_shaping].
This approach is particularly common when rewards are *sparse*, which occurs when there are few state-action pairs that have strong feedback signals.
Frequently, when researchers do not shape the rewards on sparse reward problems, the RL agent learns nothing, but reward shaping can still backfire by producing unintended agent behavior [@hadfield-menell_inverse_2020]. 
Given the nature of many conservation problems, where benefits rarely come immediately and thus the reward structures are sparse, RL agents will likely have difficulty learning anything, or, in the case that researchers shape the rewards to aid learning, the agents may learn policies that are undesirable.
Moreover, specifying a reward function for conservation brings up various ethical concerns.
E.g., who gets to specify the reward function, and will the values of the greater community be represented in the reward function?
